Analysis

### 2019-12-12 analysis.Rmd
cambie  nombre a imagenes de graficos
Los graficos de brecha segun educacion se llaman:

gapper_educ.png
gapjus_educ.png

 ggsave(table_ed_gapper,filename = "images/salario_per.png",device = "png",width = 30,height = 15,dpi = "retina",units = "cm")

@@

 ggsave(table_ed_gapjus,filename = "images/salario_per.png",device = "png",width = 30,height = 15,dpi = "retina",units = "cm")
```

>>>>

 ggsave(table_ed_gapper,filename = "images/gapper_educ.png",device = "png",width = 30,height = 15,dpi = "retina",units = "cm")

@@

 ggsave(table_ed_gapjus,filename = "images/gapjus_educ.png",device = "png",width = 30,height = 15,dpi = "retina",units = "cm")
```
